\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{microtype}

\author{Tushaar Kamat}
\title{20.08 Reflections}

\begin{document}
\maketitle

\begin{enumerate}
\item Think back to when you decided to take AP Computer Science.
  \begin{itemize}
  \item What were your reasons for taking the course?
  \item Describe what you used to think computer science was all about.
  \item What did you think you were going to learn?
  \end{itemize}

  Ever since the day I was given an ancient Nintendo Gameboy when I was 6 or 7,
  I have always had a deep interest in computers, and how they worked. When I
  learned that there was a Computer Science class available on FLVS, I
  immediatly jumped at the opportunity to take it. I already knew a little bit
  about computer science before, since I had taken an online Javascript class
  for fun, and I assumed Java would be similiar. (They both have Java in their
  name after all!) I was completely mistaken however, and learning Java has been
  a lot different than I initially expected. I completely fell in love with the
  object-oriented programming model, and the class as a whole was very
  interesting and engaging! 

\item Consider how far you have come from your first HelloWorld.java program.
  \begin{itemize}
  \item Today, if someone asked you what computer science is about, what would you
  say?
  \item Describe some things that you learned that surprised you during the
  course.
  \item When you think about the future, in what ways are you better or less
  prepared to deal with technology issues that may affect you personally or
  society in general?
\end{itemize}

  If someone asked me what computer science is about, I would tell them it is
  about using your brain and a foreign language to communicate ideas to a computer
  with the intent of solving a problem. While computer science makes many people
  think of random, endless streams of meaningless numbers and symbols; it is
  really a lot more thoughtful and challenging. One thing that surprised me was
  realizing how 

\item Describe a lesson that was challenging or interesting. What was it about
  the lesson that made it memorable?

\item Describe a lesson that you would like to see changed. Make a specific
  recommendation to improve this lesson.

\item What career possibilities do you see for yourself in the future? How might
  technology be involved?
\end{enumerate}

\end{document}
